A pipeline to analyse time-course gene expression data

### 2020-06-17 scripts/manuscript.Rmd
FIX citation

The first steps of analysis of gene expression data is always to do
normalization and quality control checks of the data. However, in what follows, we do not show the steps for normalization, as these are specific to the platform (microarray); the code for the normalization can be found in as a supplemental file [@abrams:protocol] [@park:evalution].

>>>>

The first steps of analysis of gene expression data is always to do
normalization and quality control checks of the data. However, in what follows, we do not show the steps for normalization, as these are specific to the platform (microarray); the code for the normalization can be found in as a supplemental file [@abrams:protocol; @park:evalution].
